---
title: "R Notebook"
output: html_notebook
---
# Introduction  
Visualization of levels of *CSPG4* across sites of resection/biopsy for TCGA-SKCM.  
TPM data source - xenabrowser.net.  
# Setup  
## Libraries  
```{r}
library("dplyr")
library("stringr")
library("ggplot2")
```
## Data  
### Phenotype  
Demographics data for SKCM, with information about site of resection or biopsy.
```{r}
TCGA_SKCM_phenotype = read.csv("../input/SKCM_TP_TM_demo_combined_sub.csv", row.names = 1)
head(TCGA_SKCM_phenotype)
```
### Gene expression  
TPM normalized data for TCGA-SKCM dataset.  
```{r}
TCGA_SKCM = readRDS("../input/TCGA_SKCM_GEX_phenotype_sub.RDS")
TCGA_SKCM[1:5,1:10]
```

# Pre-processing  
Combining the detailed demographics with the GEX dataset, and selecting *CSPG4*.  
```{r}
TCGA_SKCM$sample = str_sub(TCGA_SKCM$sample, 1, 12)
common_IDs = Reduce(intersect, list(TCGA_SKCM$sample, TCGA_SKCM_phenotype$submitter_id))

rownames(TCGA_SKCM_phenotype) = TCGA_SKCM_phenotype$submitter_id
rownames(TCGA_SKCM) = TCGA_SKCM$sample

TCGA_SKCM_phenotype = TCGA_SKCM_phenotype[common_IDs,]
TCGA_SKCM = TCGA_SKCM[common_IDs,]
identical(rownames(TCGA_SKCM_phenotype), rownames(TCGA_SKCM))
```

```{r}
TCGA_SKCM = cbind(TCGA_SKCM_phenotype, TCGA_SKCM)
TCGA_SKCM = TCGA_SKCM %>% select(CSPG4, type)
head(TCGA_SKCM)
```
# Visualization  
```{r}
ggplot(TCGA_SKCM, aes(y=log2(CSPG4+1), x=type)) + geom_violin() + geom_boxplot(width=0.2) + theme_minimal() + ggtitle("CSPG4 in TCGA-SKCM")
```
```{r}
sessionInfo()
```








